Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-05-11 ReviewerComments.tex
Make Reviewers' Comments consistent with current manuscript.

Writing: The multiplicity of mathematical explicit meanings for the word ``mixture" may result confusing. The distinction between the mixture component a la Farnsworth et al and the N-mixture models (e.g. binomial counts with N~pois and p random) is clear to me, but it may not be for some of JABES' audience.  I suggest re-shaping the introduction to that effect. 
\begin{quote}
In the Introduction, we now clearly refer to a practice of modeling the TTDD ``as a mixture of two distributions --- a continuous-time distribution and a point mass for increased detection probability in the initial observation period."
We define our use of `mixture model' later in the paragraph:  ``We apply the term `mixture model' to any model with a mixture TTDD."
This is contrasted in our definition of `N-mixture model' in the next paragraph: ``a hierarchical framework for multinomial counts called an N-mixture model [\dotso] --- which is an entirely different use of `mixture' from the mixture models in the previous paragraph."
\jarad{We might not need the ``which..''.}
\end{quote}

>>>>

Writing: The multiplicity of mathematical explicit meanings for the word ``mixture" may result confusing. The distinction between the mixture component a la Farnsworth et al and the N-mixture models (e.g. binomial counts with N~pois and p random) is clear to me, but it may not be for some of JABES' audience.  I suggest re-shaping the introduction to that effect. 
\begin{quote}
In the Introduction, we now clearly refer to a practice of modeling the TTDD ``as a mixture of two distributions --- a continuous-time distribution and a point mass for increased detection probability in the initial observation period."
We define our use of `mixture model' later in the paragraph:  ``[We] apply the term \emph{mixture TTDD} when the TTDD has a discrete and continuous component."
This is contrasted in our definition of `N-mixture model' in the next paragraph: ``a hierarchical framework for multinomial counts called an N-mixture model \mbox{[\dotso]}, which is an entirely different use of `mixture' from the mixture models in the previous paragraph."
\end{quote}
